State of the Practice for Medical Imaging Software

### 2022-10-13 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Revisions to MI for SOP, mainly in recommendationss

@@

\wss{CHECK  THESE, after writing all the PPs} \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers:
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) \wss{Actually mentioned by MI software},
reproducibility, and software scope determination. Although MI developers did
not mention these pain points, we cannot conclude that they are not relevant for
MI software development, since we only interviewed nine developers for about
an hour each.

@@

\begin{enumerate}
\item \textbf{Maintainability:} Although not explicitly highlighted as a pain
point during our interviews, \citet{Nguyen-HoanEtAl2010} rate maintainability as
the third most important software quality for research software in general. The push for
sustainable software \citep{deSouzaEtAl2019} is motivated by the pain that past
developers have had with accumulating too much technical debt
\citep{KruchtenEtAl2012}.  For LBM software, \citet{SmithEtAl2022} identifies
technical debt as one of the developer pain points.

@@

\item \textbf{Reproducibility:}  Although the MI developers did not mention
reproducibility explicitly as a pain point, they did mention the need to improve
documentation.  Good documentation doesn't just address the pain points of lack
of developer time (\ppref{P_LackDevTime}), technology hurdles
(\ppref{P_TechnologyHurdles}), usability \ppref{P_Usability}, and
Maintainability.  Documentation is also necessary for reproducibility. The
challenges of inadequate documentation are a known problem for research software
\citep{PintoEtAl2018, WieseEtAl2019} and for non-research software
\citep{LethbridgeEtAl2003}.

@@

This section presents our recommendations on MI software development. Although
our focus is on MI software, unless noted otherwise, our recommendations apply
to any scientific computing software.
Section~\ref{sec_recommendations_qualities} discusses the actions that can
potentially improve the ten software qualities.
Sections~\ref{sec_recommendations_limited_resources},
\ref{sec_recommendations_tech_stack}, and
\ref{sec_recommendations_testing_dataset} are based on the primary pain points
(from Section~\ref{painpoints}) collected from developers in the
MI domain.

\subsection{Recommendations on Improving Software Qualities}
\label{sec_recommendations_qualities}

@@

Based on our quality measurements in Section~\ref{ch_results} and discussions
with the developers in Section~\ref{painpoints}, we collected key points for
improving software qualities. These points should be considered for new and
existing projects, but we are not saying that every project should do everything
on our list.  All projects will have finite resources, so strategies will have
to be selected that provide the greatest return on investment.  Our specific
recommendations for each quality are as follows:

@@

>>>>

\newcounter{qnum} %quality number
\newcommand{\qthepnum}{Q`'\theqnum}
\newcommand{\qref}[1]{Q\ref{#1}}

@@

\wss{CHECK  THESE, after writing all the PPs} \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers:
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) \wss{Actually mentioned by MI software},
reproducibility, and software scope determination. Although MI developers did
not mention these pain points, we cannot conclude that they are not relevant for
MI software development, since we only interviewed nine developers for about
an hour each.  \wss{Add LBM pain points not covered.}

@@

\begin{enumerate}
\item[Q\refstepcounter{qnum}\theqnum \label{Q_Maintainability}:]
\textbf{Maintainability:} Although not explicitly highlighted as a pain point
during our interviews, \citet{Nguyen-HoanEtAl2010} rate maintainability as the
third most important software quality for research software in general. The push
for sustainable software \citep{deSouzaEtAl2019} is motivated by the pain that
past developers have had with accumulating too much technical debt
\citep{KruchtenEtAl2012}.  For LBM software, \citet{SmithEtAl2022} identifies
technical debt as one of the developer pain points.

@@

\item[Q\refstepcounter{qnum}\theqnum \label{Q_Reproducibility}:]
\textbf{Reproducibility:}  Although the MI developers did not mention
reproducibility explicitly as a pain point, they did mention the need to improve
documentation.  Good documentation doesn't just address the pain points of lack
of developer time (\ppref{P_LackDevTime}), technology hurdles
(\ppref{P_TechnologyHurdles}), usability \ppref{P_Usability}, and
Maintainability.  Documentation is also necessary for reproducibility. The
challenges of inadequate documentation are a known problem for research software
\citep{PintoEtAl2018, WieseEtAl2019} and for non-research software
\citep{LethbridgeEtAl2003}.

@@

This section presents our recommendations on MI software development. Although
our focus is on MI software, unless noted otherwise, our recommendations apply
to any scientific computing software.

In this section we provide recommendations to address the pain points from
Section~\ref{painpoints} to answer~\rqref{RQ_Recommend}.  Our recommendations
are not lists of criticisms for what should have been done in the past, or what
should be done now; they are suggestions for consideration in the future. We
will not be repeating previously discussed ideas here, such as CI, documentation
of APIs, etc.  Our aim is to mention ideas that are at least somewhat beyond
conventional best practices. The ideas listed here have the potential to become
best practices in the medium to long-term. The ideas in the following
subsections are roughly in the order of increasing implementation effort.

\subsection{Continuous Integration} \label{Sec_ContinuousIntegration}

Continuous integration is the process of building and testing software on every
push to the code repository, with pushes done very frequently \citep[p.\ 13]
{HumbleAndFarley2010}, \citep{ShahinEtAl2017, Fowler2006}.  CI consists of the
following elements:
\begin{itemize}
	\item A version control system \citep{Fowler2006}. To be effective, all
	files should be under version control, not just code files.  Anything that
	is needed to build, install and run the software should be under version
	control, including configuration files, build scripts, test harnesses, and
	operating system configurations \citep[p. 19]{HumbleAndFarley2010}.
	Fortunately for the LBM domain, as discussed above, most alive projects
	(73\% of those assessed) use version control.
	\item A fully automated build system \citep{Fowler2006}.  As \citet[p.\
	5]{HumbleAndFarley2010} point out, deploying software manually is an
	anti-pattern.  Fortunately, as discussed above, most LBM projects use build
	automation.
	\item An automated test system \citep{Fowler2006}. Building quality software
	involves creating automated tests at the unit, component, and acceptance
	test level, and executing these tests whenever someone makes a change to the
	code, its configuration, the environment, or the software stack that it runs
	on \citep[p.\ 83]{HumbleAndFarley2010}. As Table~\ref{artifactspresent}
	shows, test cases are in the uncommon category for LBM software artifacts,
	which means that some LBM projects will need to increase their testing
	automation if they wish to pursue CI.  The usual advice for CI is to keep
	the build and test process short \citep[p.\ 60]{HumbleAndFarley2010}. Given
	that LBM can be computationally expensive, the tests run with every check-in
	may need to focus on simple code interface tests, saving large tests for
	less frequent runs.  A more sophisticated option to address the bottleneck
	for merges is CIVET (Continuous Integration, Verification, Enhancement, and
	Testing), which solves this problem by intelligently pinning, cancelling,
	and if necessary, restarting jobs as merges occur \citep{SlaughterEtAl2021}.
	\item An automated system for other tasks, such as code checking,
	documentation building and web-site updating.  These other tasks are not
	essential to CI, but they can be incorporated to improve the quality
	of the code and the communication between developers and users. For
	instance, a static analysis (possibly via linters) of the code may find poor
	programming practice or lack of adherence to adopted coding standards.
	\citet{SlaughterEtAl2021} provides another example of an automated task ---
	checking that a test specification includes the test's motivation, a test
	description, and a design description for all changes. 
	\item An integration build system to pull everything together.  Every time
	there is a check-in (for instance a pull request), the integration server
	automatically checks out the sources onto the integration machine, starts a
	build, runs tests, and informs the committer of the results. 
\end{itemize}

Although CI can take some time and effort to set up and integrate into a team's
workflow, the benefits can be significant, as follows:

\begin{itemize}
	\item Elimination of headaches associated with a separate integration phase
	\citep{Fowler2006}, \citep[p.\ 20]{HumbleAndFarley2010}. If integration of
	the work of different developers, or even separate chunks of work by the
	same developer, is postponed, integration problems are inevitable.  By
	continuously integrating, problems are immediately obvious and the source of
	the problem can be isolated to the small increment that was just committed.
	\item Bugs can be quickly detected and removed \citep{Fowler2006} via
	automated testing.  To improve productivity, defects are best discovered and
	fixed at the point where they are introduced \citep[p.\
	23]{HumbleAndFarley2010}.  Code is not the only source of errors; they are
	also found in the files and scripts related to configuration management
	\citep[p.\ 18]{HumbleAndFarley2010}.
	\item Developers are always working on a stable base, since the master
	branch will always be working.  A stable base passes all tests and, if the
	CI system uses generators and linters, it will also have current
	documentation and coding standard compliant code.  A stable base improves
	developer productivity, allowing them to focus on coding, testing, and
	documentation.
\end{itemize}

Although there are still challenges, setting up a CI system has never been
easier than it is today.  The option of installing a dedicated CI server (either
physically or virtually) exists with tools such as
\href{https://www.jenkins.io/} {Jenkins}, \href{http://buildbot.net/}
{Buildbot}, \href{https://www.gocd.org/} {Go}, and
\href{http://integrity.github.io/} {Integrity}. However, installation on your
own server is unnecessary since there are many hosted CI tool solutions
available, such as: \href{https://travis-ci.org/} {Travis CI},
\href{https://github.com/features/actions} {GitHub Actions} and
\href{https://circleci.com/} {CircleCI}.  Getting started with a hosted CI is
straightforward.  All that is required to begin is editing a few lines of a YAML
configuration file in the project's root directory.

Challenges that exist for adopting CI include lack of awareness and
transparency, coordination and collaboration challenges, lack of expertise and
skills, more pressure and workload for team members, general resistance to
change, scepticism and distrust on continuous practices \citep{ShahinEtAl2017}.
The most common reason given for not adopting CI is that developers on my
project are not familiar enough with CI \citep{HiltonEtAl2016}.  These problems
can be mitigated via planning and documentation, promoting a team mindset,
adopting new rules and policies, improving testing activities, and decomposing
development into smaller units \citep{ShahinEtAl2017}.

\subsection{Employ Linters} \label{Sec_Linters}

Except for \citet{ThielEtAl2020}, the research software guidelines that we
consulted do not mention linters.  However, we believe that linters have the
potential to improve code quality at a relatively low cost.  A linter is a tool
that statically analyzes code to find programming errors, stylistic
inconsistencies and suspicious constructs \citep{Wikipedia2022_Lint}. Linters
can be used to spot check code files, or even better as part of a continuous
integration system, as discussed in Section~\ref{Sec_ContinuousIntegration}.

A sample of the potential benefits of linters include: finding memory leaks,
finding potential bugs, standardizing code with respect to formatting, improving
performance, removing silly errors before code reviews, and catching potential
security issues \citep{SourceLevel2022_Lint}.  Linters are available for most
popular programming languages.  For instance Python has the options of PyLint,
flake8 and Black \citep{Zadka2018}.

Linters can address the pain points for LBM developers.  For instance, a linter
can decrease the amount of development time (\ppref{P_LackDevTime}) by
decreasing the number of mundane mistakes programmers have to catch.  Since the
linter can include rules that capture the wisdom of senior programmers, it can
help newer developers avoid common mistakes. Although there are not many linters
for checking parallel programming mistakes (\ppref{P_TechnologyHurdles}),
Parallel Lint is an option for OpenMP. Consistently using a linter can guard
against some technical debt (\ppref{Q_Maintainability}). Although linters are
tools for code analysis, similar ideas can be applied to ``lint'' documentation
to ensure adherence to basic rules.  The use of tools to check documentation is
a partial explanation for the relatively higher quality of statistical tools
that are part of the Comprehensive R Archive Network (CRAN)
\citep{SmithEtAl2018_StatSoft}.

\subsection{Conduct Rigorous Peer Reviews} \label{Sec_PeerReview}

Peer review is a strategy already adopted by some LBM developers to improve
confidence in their software, but the benefits of peer review can be improved by
making its application more rigorous. \citet{Jones2008} shows that rigorous
inspection finds 60-65\% of latent defects on average, and often tops 85\% in
defect removal efficiency.  By way of comparison, most forms of testing average
between 30 and 35\% for defect removal efficiency \citep{EbertAndJones2009,
Jones2008}.  A formal code inspection involves asking the reviewer to either
follow a review checklist (check consistency of variable names, look for
terminating loops, etc.), or perform specific review tasks (like summarize the
purpose of the code, create a data dictionary for a given module,
cross-reference the code to the technical manual, etc.) The task based
inspection approach has been effectively used for research software, as
described by \citet{KellyAndShepard2000}. Task based inspection is an ideal fit
with an issue tracking system, like GitHub.  The review tasks can be issues, so
that they can be easily assigned, monitored and recorded.  Other potential
issues for the tracker include assigning junior team members to test
installation instructions and getting-started tutorials.

Rigorous peer review addresses the same pain points as linters
(Section~\ref{Sec_Linters}): \ppref{P_LackDevTime}, \ppref{P_TechnologyHurdles},
and \ppref{Q_Maintainability}. Peer review addresses these points by efficiently
searching for defects and problems.  Finding misunderstandings in of how the
code implements the required theory improves the software's correctness
(\ppref{P_Correctness}).

@@

@@

\subsection{Follow Advice From the Open-Source Community to Grow the Number of Contributors} \label{Sec_GrowContributors}

In our interviews with developers we heard they would like to have additional
software contributors.  More developers would help with addressing the lack of
development time pain point (\ppref{P_LackDevTime}).  In investigating advice on
increasing the number of contributors, we found that the advice usually starts
with following best practices, including providing artifacts like those
discussed in Section~\ref{Sec_CompareArtifacts}, such as a contributor
guidelines, code style guidelines, a clear code of conduct and high quality code
and documentation. This advice is logical, but in our assessment of LBM software
we found examples of projects that already follow many best practices, but still
have small development teams. Attracting developers apparently requires more
than just building a good product.

Some potential additional ideas for growing the number of contributors are
as follows:

\begin{itemize}
	\item Clearly identify issues that are an appropriate starting points for
	new developers \citep{Garcia2016, Jalan2016, Proffitt2017}.
	\item Given that in most projects developers were once users
	\citep{McQuaid2018}, recruit future developers from the current set of
	users.
	\item Create templates for pull requests and issues \citep{Jalan2016}.
    \item Welcome all kinds of contributions, not just code.  Non-code
    contributions include documentation, fixing typos, issue reporting and test
    cases \citep{Jalan2016, Proffitt2017}.
    \item Reward and recognize new contributors, via small rewards like stickers
    or shirts, or even just a simple shoutout or mention in a blog post or on
    social media \citep{Jalan2016, Proffitt2017}.
    \item Recognize that open source is more about people than it will ever be
    about code \citep{Jalan2016}.
    \item Look beyond just recruiting online and seek new developers at
    conferences or other user meet ups \citep{Garcia2016}.
    \item Follow the advice of \citet{Kuchner2012} to adapt ideas from marketing
    to promote science.  Specific ideas that could be applied to open source
    projects include the following: 
    \begin{itemize}
		\item Storytelling to motivate interest in the project, where the story
		is a sequence of events and pauses for reflection \citep[p.\
		21--22]{Kuchner2012}.
		\item Invest effort in building relationships with users and with potential future developers.
		\item Brand your project with what makes it unique and special.
	\end{itemize}
	\item Consider combining existing projects to pool collective resources, and
	reduce competition between different open source projects.
\end{itemize}

\subsection{Design For Change} \label{Sec_DesForChange}

To address technical debt (\ppref{Q_Maintainability}), the top LBM developers show how
modularization can be used to design research software for future change.
Although the advice to modularize research software to handle complexity is
common \citep{WilsonEtAl2014, StewartEtAl2017, Storer2017}, specific guidelines
on how to divide the software into modules is less prevalent.  Not every
decomposition is a good design for supporting change, as shown by
\citet{Parnas1972a}.  A design with low cohesion and high coupling \citep[p.\
48]{GhezziEtAl2003} will make change difficult. Especially in research software,
where change is inevitable, designers need to produce a modularization that
supports change. Ocean modelling software is currently feeling the pain of
not emphasizing modularization in legacy code \citep{JungEtAl2022}.

Interviewed LBM developers highlighted cases where their modularizations
anticipated future changes.  The developer of pyLBM mentioned that the
geometries and models of their system had been ``decoupled'', using abstraction
and modularization of the source code, to make it ``very easy to add [new]
features''.  The pyLBM design allows for independent changes to the geometry and
the model.  We also learned that the package pyLBM redeveloped data structures
to ease future changes. The developer of TCLB noted that their design allows for
the addition of some LBM features, but changes to major aspects of the system
would be difficult. For example, ``implementing a new model will be an easy
contribution'', but changes to the ``Cartesian mesh … will be a nightmare''. The
design of TCLB highlights that not every conceivable change needs to be
supported, only the likely changes.

As the LBM developers illustrate, they accomplish design for change by first
identifying likely changes, either implicitly or explicitly, and second by
hiding each likely change behind a well-defined module interface.  Although it
is unclear whether the developers are aware of Parnas's work, the approach
mirrors his recommendations \citep{Parnas1972a}. \citet{SmithEtAl2022} (Section
Documentation as Part of the Development Process) lists ideas for how to
document the design, including the likely changes, so that they are more visible
to others.

\subsection{Assurance Case} \label{AssuranceCases}

From \cite{RinehartEtAl2015}, an assurance case is ``[a] reasoned and compelling
argument, supported by a body of evidence, that a system, service or
organization will operate as intended for a defined application in a defined
environment.''  Assurance cases have been successfully employed for safety
critical systems, but using this technique for SC software is a new idea.  The
Goal Structuring Notation (GSN) \cite{Spriggs2012} seems like a good framework
for initial investigation.

Scientific software, such as medical software, is often subject to
standardization and regulatory approval. While applying such approvals and
standards has had a beneficial effect on system quality, it does not provide
good tracking of the development stages, as the compliance with the standards
is mostly checked after the system development. Once a system is implemented,
its documentations must be approved by the regulators. This process is lengthy
and expensive. In contrast, assurance case development usually occurs in
parallel with the system construction, resulting in a traceable, detailed
argument for the desired property.  Moreover, since the assurance case is
integrated into the system construction, the domain experts are involved from
the start.

Putting the argument in the hands of the experts means that they will work to
convince themselves, along with the regulators.  They will use the expertise
that the regulators do not have and they will see the value of documentation (as
mentioned in section on pain points with methods to mitigate); they will be
engaged.  This engagement will hopefully help bridge the current chasm between
software engineering and scientific computing~\cite{Kelly2007}, by motivating
scientists toward documentation and correcting the problem of software engineers
failing to meet scientists' expectations~\cite{Segal2008}.  Significant
documentation will still likely be necessary, but now the developers control the
documentation.  What is created will be relevant and necessary.

For SCS a top level claim could read ``Program X delivers correct outputs when
used for its intended use/purpose in its intended environment.''  The next step
would be to decompose this claim into sub-claims that will be easier to prove.
The sub-claims will likely also be further divided until the bottom of the
graph, where the measurable evidence is provided.  Typical evidence will consist
of documents, expert reviews, test case results etc.

Using the specific example of preparing an assurance case for pre-existing
medical image analysis software (3dfim+)~\cite{SmithEtAl2018_ICSEPoster}, the
top level can be decomposed into four sub-goals, as shown in
Figure~\ref{TopGoal}.  This example follows the same pattern as used for medical
devices~\cite{Wassyng2015}.  The first sub-goal (GR) argues for the quality of
the documentation of the requirements (SRS).  The second sub-goal (GD) says that
the design complies with the requirements and the third proposes that the
implementation also complies with the requirements.  The fourth sub-goal (GA)
claims that the inputs to 3dfim+ will satisfy the operational assumptions, since
we need valid input to make an argument for the correctness of the output.

\begin{figure*}[!h]
\centering
\includegraphics[width=1.0\textwidth]{./figures/TopGoal.pdf}
\caption{Top Goal of the assurance case and its sub-goals}
\label{TopGoal}
\end{figure*}

Preparing an assurance case for the pre-existing 3dfim+ software justifies the
value of assurance cases for the certification of SCS~\cite{SmithEtAl2018}.
Although no errors were found in the output of the existing software, the rigour
of the proposed approach did lead to finding ambiguities and omissions in the
existing documentation, such as missing information on the coordinate system
convention.  In addition, a potential concern for the software itself was
identified from the GA argument: running the software does not produce any
warning about the obligation of the user to provide data that matches the
parametric statistical model employed for the correlation calculations.

Potential objectives for research on assurance cases applied to SCS are as
follows:

\begin{enumerate}
\item Creation of an assurance case template will require looking at a variety
  of SCS projects, which will require engaged project partners; therefore, the
  initial approach should be to target domains where certification is required,
  or domains where verification is critical, but challenging, like the High
  Energy Physics (HEP). \wss{reference the paper about domain specific
  methodology - maybe I already did?}
\item Evidence is provided at the bottom of an assurance case, but what is
  the best form for this evidence?  As mentioned for the SRS, we need an
  approach for verification.  We also need an approach to verify the other
  software artifacts, the traceability between them, the team of developers, the
  team of reviewers, etc.  The question for the future is what combination of
  tools and processes will provide convincing evidence?
\item Creation of assurance cases is challenging with existing tools.  In the
  future, the goal should be automatic generation (see
  \citet{Smith2018}, Section SecAutoGenerate) of the visual assurance case documentation from
  the arguments and evidence
\item Creating a revelation on the value of documentation \citep{Smith2018} may
   require a pseudo adversarial approach.  SCS developers should be explicitly
   challenged to present their verification efforts so that their work can be
   independently verified.  Although SCS developers have developed many
   successful theories, techniques, and testing procedures for verification, the
   evidence is generally presented in an ad hoc manner.  Developers should be
   asked to connect all the pieces of their evidence in a coherent argument.  As
   a bonus, the act of creating the assurance case may also lead developers to
   discover subtle edge cases, which would not have been noticed with a less
   rigorous and systematic approach.

\subsection{Generate All Things} \label{Sec_GenAllThings}

We propose automatically generating LBM code and its documentation, using a
Domain Specific Modelling (DSM) approach. DSM means creating a knowledge base of
models for physics, computing, mathematics, documentation, and certification and
then writing explicit ``recipes'' that weave together this knowledge to generate
the desired code, documentation, test cases, inspection reports and build
scripts. This definition of DSM is more general than usual; in this
recommendation DSM implies generation of all software artifacts, not just the
code. DSM moves development to a higher level of abstraction; domain experts can
work without concern for low-level implementation details. Using DSM, we
optimally generate code and documentation, eliminate redundancy, reduce the
likelihood of errors, and automate maintenance. Moreover, a generative approach
facilitates the inevitable exploration of LBM modelling assumptions.

DSM provides a transformative technology for documentation, design, and
verification \citep{JohansonAndHasselbring2018, Smith2018}. DSM allows
scientists to focus on their science, not software.  A generative approach
removes the maintenance nightmare of documentation duplicates and near
duplicates \citep{LucivEtAl2018}, since developers capture knowledge once and
transform it as needed.  Code generation has previously been applied to improve
research software.  For instance, ATLAS (Automatically Tuned Linear Algebra
Software) \citep{WhaleyEtAl2001} and Blitz++ \citep{Veldhuizen1998} produces
efficient and portable linear algebra software.  Spiral \citep{Pueschel2001}
uses software/hardware generation for digital signal processing.
\citet{Carette2008} shows how to generate a family of efficient, type-safe
Gaussian elimination algorithms.  FEniCS (Finite Element and Computational
Software) uses code generation when solving differential equations
\citep{LoggEtAl2012}. \citet{OberEtAl2018} and \citet{MatkerimEtAl2013} apply
DSM to High Performance Computing (HPC), using UML (Unified Modelling Language)
for their domain models. Unlike previous DSM work, the current recommendation
focuses on generating all software artifacts (requirements, design, etc.), not
just code.  \citet{SzymczakEtAl2016} presents initial work on this ``generate
all things'' approach, \citet{SmithAndCarette2021-BRIC} presents a motivating
example, and \citep{CaretteEtAl2021-Drasil} provides a prototype.

A DSM approach addresses multiple pain points.  For instance, once the
infrastructure is in place, a DSM can decrease the amount of development time
(\ppref{P_LackDevTime}) by automation.  Since a DSM approach allows scientists
to focus on their science, rather than software, the lack of software
development experience will be less of an issue. The DSM approach can capture
computing knowledge to mitigate the technology related pain points
(\ppref{P_TechnologyHurdles}).  For ensuring correctness (\ppref{P_Correctness})
a generative approach can aim to be correct by construction.  If there are
mistakes, DSM has the advantage that they are propagated throughout the
generated artifacts, which greatly increases the chance that someone will notice
the mistake.  Technical debt (\ppref{Q_Maintainability}) is not a concern with a
DSM approach since developers write the recipes used for generation at a high
level making them relatively easy to change.  With respect to pain points on
usability (\ppref{P_Usability}), the generative approach we are proposing
addresses these directly, since documentation is a primary concern, rather than
an afterthought.
